Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-05-02 Manuscript.Rmd
only 4 discussion pts left

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013a], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far. Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide brain regions that show overlap of DN and valuation effects into DN and non-DN in 100 individuals. Restricting our analyses to this general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis. Unlike some popular clustering algorithms, SP has the advantage of determinisitcally partitioning networks. Comparisons with modularity maximization suggested the binary partitioning was appropriate.

The community structure identified by SP was idiosyncratic across individuals, and stable across test/re-test evaluations within-individuals. We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.

@@

  - The community structure identified by SP was reliable across test/re-test and was heterogeneous across individuals. The heterogeneity was especially large in mPFC.

  - There are various potential sources of the heterogeneity. Could be gross anatomy (varying sulcal patterns; Mackey). Could also be shifts in function relative to anatomy (Haxby hyperalignment). Could be connectivity (Passingham, Mars, Tobyne). A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture (Glasser), or structural connectivity/white matter microstructure (Saygin & Kanwisher).

   - SP is data-driven and the communities don't come with labels. We applied labels based on the meta-analysis. We were able to apply group-level labels on the basis of the topography in PCC, where functional organization was more consistent across individuals. Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.

  - Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio (fewer individuals and more data per individual; Gordon, Braga, Poldrack). We've been able to quantify the variability in a large sample, and our method does not require massively multi-session data acquisition.

@@

```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B from Braga et al. (2019) and SP communities for two individuals. Upper: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders. Bottom: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either DN sub-network."}

>>>>

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far. Therefore, affirming that among DN and valuation share neural substrates in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Tian2018]. For 100 individuals, we reliably subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities. Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis. Partitioning an individual's brain network through SP has a number of advantages, such as identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e. preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness and separability of a network through examination of its resulting eigenvalues (**TODO: show this in text**) [@chung1997; @Tian2018]. Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities, suggested the binary partitioning was appropriate.

We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC. However, the precise spatial organization of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individuals. This idiosyncrasy in functional topography was particularly pronounced in mPFC, and was present with various amounts of data.

The degree of individual-specifitcity observed in this work can arise from a variety of sources. For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to systematically vary across individuals [@Mackey2014]. Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018]. A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Saygin2016].

Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities. We circumvented this issue by identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially affiliated to the DN literature in the meta-analysis. We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals. Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.

Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio [fewer individuals and more data per individual; Gordon, Braga, Poldrack]. While inter-individual differences in functional topography have been described in these studies, here we were able to quantify the variability in a large sample. and our method does not require massively multi-session data acquisition.

@@

@@

```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B from Braga et al. (2019) and SP communities for two individuals. Upper: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders. Correlation values are thresholded at 0.2. Bottom: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either DN sub-network."}
